\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2019-07-22 analysis/paper/paper.Rmd
Merge with master following the change to a new directory structure

---
documentclass: jss
author:
  - name: Sahir Bhatnagar *
    affiliation: McGill Univeristy
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{sahir.bhatnagar@mail.mcgill.ca}
    url: http://sahirbhatnagar.com/
  - name: Maxime Turgeon *
    affiliation: University of Manitoba
    address: >
      318 Machray Hall
      Winnipeg, MB, Canada R3T 2N2
    email: \email{max.turgeon@umanitoba.ca}
    url: http://maxturgeon.ca/
  - name: Jesse Islam 
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{jesse.islam@mail.mcgill.ca}
  - name: James Hanley
    affiliation: McGill Univeristy
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{james.hanley@mcgill.ca}
    url: http://www.medicine.mcgill.ca/epidemiology/hanley/
  - name: Olli Saarela
    affiliation: University of Toronto
    address: >
      Dalla Lana School of Public Health, 
      155 College Street, 6th floor, 
      Toronto, Ontario 
      M5T 3M7, Canada
    email: \email{olli.saarela@utoronto.ca}
    url: http://individual.utoronto.ca/osaarela/
title:
  formatted: "\\pkg{casebase}: An Alternative Framework For Survival Analysis"
  # If you use tex in the formatted title, also supply version without
  plain:     "casebase: An Alternative Framework For Survival Analysis"
  # For running headers, if needed
  short:     "\\pkg{casebase}: An Alternative Framework For Survival Analysis"
abstract: >
  The abstract of the article. * joint co-authors
keywords:
  # at least one keyword must be supplied
  formatted: [keywords, not capitalized, "\\proglang{Java}"]
  plain:     [keywords, not capitalized, Java]
preamble: >
  \usepackage{amsmath}
  \usepackage{longtable}
output: 
  rticles::jss_article:
    number_sections: TRUE     #added argument option 
    citation_package: "natbib"  #All my citations use biblatex, not natbib. 
biblio-style: jss      #Listed to use in JSS Instructions for Authors, but not in template by default. 
bibliography: references.bib  #Also not included in template by default. 
fig_width: 7
fig_height: 6
fig_caption: true
---

@@

```{r erspc-casebase-splines, eval = eval_cs1}
casebase_splines <- fitSmoothHazard(DeadOfPrCa ~ splines::bs(Follow.Up.Time) + ScrArm, 
                                    data = ERSPC, 
                                    ratio = 100)

>>>>

---
documentclass: jss
author:
  - name: Sahir Bhatnagar *
    affiliation: McGill Univeristy
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{sahir.bhatnagar@mail.mcgill.ca}
    url: http://sahirbhatnagar.com/
  - name: Maxime Turgeon *
    affiliation: University of Manitoba
    address: >
      186 Dysart Road
      Winnipeg, MB, Canada R3B 0S8
    email: \email{max.turgeon@umanitoba.ca}
    url: https://maxturgeon.ca/
  - name: Jesse Islam 
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{jesse.islam@mail.mcgill.ca}
  - name: James Hanley
    affiliation: McGill Univeristy
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{james.hanley@mcgill.ca}
    url: http://www.medicine.mcgill.ca/epidemiology/hanley/
  - name: Olli Saarela
    affiliation: University of Toronto
    address: >
      Dalla Lana School of Public Health, 
      155 College Street, 6th floor, 
      Toronto, Ontario 
      M5T 3M7, Canada
    email: \email{olli.saarela@utoronto.ca}
    url: http://individual.utoronto.ca/osaarela/
title:
  formatted: "\\pkg{casebase}: An Alternative Framework For Survival Analysis"
  # If you use tex in the formatted title, also supply version without
  plain:     "casebase: An Alternative Framework For Survival Analysis"
  # For running headers, if needed
  short:     "\\pkg{casebase}: An Alternative Framework For Survival Analysis"
abstract: >
  The abstract of the article. * joint co-authors
keywords:
  # at least one keyword must be supplied
  formatted: [keywords, not capitalized, "\\proglang{Java}"]
  plain:     [keywords, not capitalized, Java]
preamble: >
  \usepackage{amsmath}
  \usepackage{longtable}
output: 
  rticles::jss_article:
    number_sections: TRUE     #added argument option 
    citation_package: "natbib"  #All my citations use biblatex, not natbib. 
biblio-style: jss      #Listed to use in JSS Instructions for Authors, but not in template by default. 
bibliography: references.bib  #Also not included in template by default. 
fig_width: 7
fig_height: 6
fig_caption: true
---

@@

```{r erspc-casebase-splines, eval = eval_cs1}
library(splines)
casebase_splines <- fitSmoothHazard(DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm,
                                    data = ERSPC, 
                                    ratio = 100)

### 2019-07-22 analysis/paper/paper.tex
Merge with master following the change to a new directory structure

\author{
Sahir Bhatnagar *\\McGill Univeristy \And Maxime Turgeon *\\McGill University \And James Hanley\\McGill Univeristy \And Olli Saarela\\University of Toronto
}
\title{\pkg{casebase}: An Alternative Framework For Survival Analysis}

\Plainauthor{Sahir Bhatnagar *, Maxime Turgeon *, James Hanley, Olli Saarela}
\Plaintitle{casebase: An Alternative Framework For Survival Analysis}
\Shorttitle{\pkg{casebase}: An Alternative Framework For Survival Analysis}

@@

\Address{
    Sahir Bhatnagar *\\
  McGill Univeristy\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{sahir.bhatnagar@mail.mcgill.ca}\\
  URL: \url{http://sahirbhatnagar.com/}\\~\\
      Maxime Turgeon *\\
  McGill University\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{maxime.turgeon@mail.mcgill.ca}\\
  URL: \url{http://maxturgeon.ca/}\\~\\
      James Hanley\\
  McGill Univeristy\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{james.hanley@mcgill.ca}\\
  URL: \url{http://www.medicine.mcgill.ca/epidemiology/hanley/}\\~\\
      Olli Saarela\\
  University of Toronto\\
  Dalla Lana School of Public Health, 155 College Street, 6th floor,
  Toronto, Ontario M5T 3M7, Canada\\
  E-mail: \email{olli.saarela@utoronto.ca}\\
  URL: \url{http://individual.utoronto.ca/osaarela/}\\~\\
  }

@@

\begin{CodeInput}
R> casebase_splines <- fitSmoothHazard(DeadOfPrCa ~ splines::bs(Follow.Up.Time) + ScrArm, 
R>                                     data = ERSPC, 
R>                                     ratio = 100)
R> 
R> summary(casebase_splines)
R> exp(coef(casebase_splines))
R> exp(confint(casebase_splines))
\end{CodeInput}
\end{CodeChunk}

@@

This report was generated on 2019-07-22 17:17:57 using the following
computational environment and dependencies:

@@

#>  version  R version 3.6.0 (2019-04-26)
#>  os       Pop!_OS 18.10               

@@

#>  language en_CA:en                    

@@

#>  tz       America/Toronto             

@@

#>  package     * version    date       lib
#>  assertthat    0.2.1      2019-03-21 [1]
#>  backports     1.1.4      2019-04-10 [1]
#>  broom         0.5.1      2018-12-05 [1]
#>  callr         3.2.0      2019-03-15 [1]
#>  casebase    * 0.1.1.9000 2019-07-22 [1]
#>  cellranger    1.1.0      2016-07-27 [1]
#>  cli           1.1.0      2019-03-19 [1]
#>  colorspace    1.4-1      2019-03-18 [1]
#>  crayon        1.3.4      2017-09-16 [1]
#>  data.table    1.12.2     2019-04-07 [1]
#>  desc          1.2.0      2018-05-01 [1]
#>  devtools      2.0.1      2018-10-26 [1]
#>  digest        0.6.20     2019-07-04 [1]
#>  dplyr       * 0.8.0.1    2019-02-15 [1]
#>  evaluate      0.14       2019-05-28 [1]
#>  forcats     * 0.4.0      2019-02-17 [1]
#>  fs            1.3.1      2019-05-06 [1]
#>  generics      0.0.2      2018-11-29 [1]
#>  ggplot2     * 3.2.0      2019-06-16 [1]
#>  glue          1.3.1      2019-03-12 [1]
#>  gtable        0.3.0      2019-03-25 [1]
#>  haven         2.1.0      2019-02-19 [1]
#>  hms           0.4.2      2018-03-10 [1]
#>  htmltools     0.3.6      2017-04-28 [1]
#>  httr          1.4.0      2018-12-11 [1]
#>  jsonlite      1.6        2018-12-07 [1]
#>  knitr         1.23       2019-05-18 [1]
#>  lattice       0.20-38    2018-11-04 [5]
#>  lazyeval      0.2.2      2019-03-15 [1]
#>  lubridate     1.7.4      2018-04-11 [1]
#>  magrittr    * 1.5        2014-11-22 [1]
#>  Matrix        1.2-17     2019-03-22 [5]
#>  memoise       1.1.0      2017-04-21 [1]
#>  mgcv          1.8-28     2019-03-21 [5]
#>  modelr        0.1.4      2019-02-18 [1]
#>  munsell       0.5.0      2018-06-12 [1]
#>  nlme          3.1-140    2019-05-12 [5]
#>  pillar        1.4.2      2019-06-29 [1]
#>  pkgbuild      1.0.3      2019-03-20 [1]
#>  pkgconfig     2.0.2      2018-08-16 [1]
#>  pkgload       1.0.2      2018-10-29 [1]
#>  prettyunits   1.0.2      2015-07-13 [1]
#>  processx      3.3.1      2019-05-08 [1]
#>  ps            1.3.0      2018-12-21 [1]
#>  purrr       * 0.3.2      2019-03-15 [1]
#>  R6            2.4.0      2019-02-14 [1]
#>  Rcpp          1.0.1      2019-03-17 [1]
#>  readr       * 1.3.1      2018-12-21 [1]
#>  readxl        1.3.0      2019-02-15 [1]
#>  remotes       2.0.2      2018-10-30 [1]
#>  rlang         0.4.0      2019-06-25 [1]
#>  rmarkdown     1.14       2019-07-12 [1]
#>  rprojroot     1.3-2      2018-01-03 [1]
#>  rstudioapi    0.10       2019-03-19 [1]
#>  rticles       0.9.1      2019-07-22 [1]
#>  rvest         0.3.2      2016-06-17 [1]
#>  scales        1.0.0      2018-08-09 [1]
#>  sessioninfo   1.1.1      2018-11-05 [1]
#>  stringi       1.4.3      2019-03-12 [1]
#>  stringr     * 1.4.0      2019-02-10 [1]
#>  survival    * 2.43-3     2018-11-26 [5]
#>  testthat      2.1.1      2019-04-23 [1]
#>  tibble      * 2.1.3      2019-06-06 [1]
#>  tidyr       * 0.8.2      2018-10-28 [1]
#>  tidyselect    0.2.5      2018-10-11 [1]
#>  tidyverse   * 1.2.1      2017-11-14 [1]
#>  usethis       1.5.0.9000 2019-06-24 [1]
#>  VGAM          1.1-1      2019-02-18 [1]
#>  withr         2.1.2      2018-03-15 [1]
#>  xfun          0.8        2019-06-25 [1]
#>  xml2          1.2.0      2018-01-24 [1]
#>  yaml          2.2.0      2018-07-25 [1]
#>  source                                  
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  Github (sahirbhatnagar/casebase@669a0eb)
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.3)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.3)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  Github (rstudio/rticles@8d56fc6)        
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  Github (r-lib/usethis@d4eabb9)          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.5.1)                          

@@

#> [1] /home/sahir/R/x86_64-pc-linux-gnu-library/3.5
#> [2] /home/sahir/R/x86_64-pc-linux-gnu-library/3.6
#> [3] /usr/local/lib/R/site-library
#> [4] /usr/lib/R/site-library
#> [5] /usr/lib/R/library

@@

\begin{CodeOutput}
#> Local:    litreview /home/sahir/git_repositories/cbpaper
#> Head:     [38153a4] 2019-07-22: Update README.md
\end{CodeOutput}
\end{CodeChunk}

>>>>

\author{
Sahir Bhatnagar *\\McGill Univeristy \And Maxime Turgeon *\\University of Manitoba \And Jesse Islam\\McGill University \And James Hanley\\McGill Univeristy \And Olli Saarela\\University of Toronto
}
\title{\pkg{casebase}: An Alternative Framework For Survival Analysis}

\Plainauthor{Sahir Bhatnagar *, Maxime Turgeon *, Jesse Islam, James Hanley, Olli Saarela}
\Plaintitle{casebase: An Alternative Framework For Survival Analysis}
\Shorttitle{\pkg{casebase}: An Alternative Framework For Survival Analysis}

@@

\Address{
    Sahir Bhatnagar *\\
  McGill Univeristy\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{sahir.bhatnagar@mail.mcgill.ca}\\
  URL: \url{http://sahirbhatnagar.com/}\\~\\
      Maxime Turgeon *\\
  University of Manitoba\\
  186 Dysart Road Winnipeg, MB, Canada R3B 0S8\\
  E-mail: \email{max.turgeon@umanitoba.ca}\\
  URL: \url{https://maxturgeon.ca/}\\~\\
      Jesse Islam\\
  McGill University\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{jesse.islam@mail.mcgill.ca}\\

      James Hanley\\
  McGill Univeristy\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{james.hanley@mcgill.ca}\\
  URL: \url{http://www.medicine.mcgill.ca/epidemiology/hanley/}\\~\\
      Olli Saarela\\
  University of Toronto\\
  Dalla Lana School of Public Health, 155 College Street, 6th floor,
  Toronto, Ontario M5T 3M7, Canada\\
  E-mail: \email{olli.saarela@utoronto.ca}\\
  URL: \url{http://individual.utoronto.ca/osaarela/}\\~\\
  }

@@

\begin{CodeInput}
R> library(splines)
R> casebase_splines <- fitSmoothHazard(DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm,
R>                                     data = ERSPC, 
R>                                     ratio = 100)
R> 
R> summary(casebase_splines)
R> exp(coef(casebase_splines))
R> exp(confint(casebase_splines))
\end{CodeInput}
\end{CodeChunk}

@@

This report was generated on 2019-07-22 16:50:40 using the following
computational environment and dependencies:

@@

#>  version  R version 3.6.1 (2019-07-05)
#>  os       Ubuntu 18.04.2 LTS          

@@

#>  language (EN)                        

@@

#>  tz       America/Winnipeg            

@@

#>  package     * version    date       lib source                          
#>  assertthat    0.2.0      2017-04-11 [1] CRAN (R 3.5.0)                  
#>  backports     1.1.2      2017-12-13 [1] CRAN (R 3.5.0)                  
#>  broom         0.4.4      2018-03-29 [1] CRAN (R 3.5.0)                  
#>  callr         3.3.0      2019-07-04 [1] CRAN (R 3.6.1)                  
#>  casebase    * 0.1.0.9000 2019-07-19 [1] local                           
#>  cellranger    1.1.0      2016-07-27 [1] CRAN (R 3.5.0)                  
#>  cli           1.1.0      2019-03-19 [1] CRAN (R 3.6.1)                  
#>  colorspace    1.3-2      2016-12-14 [1] CRAN (R 3.5.0)                  
#>  crayon        1.3.4      2017-09-16 [1] CRAN (R 3.5.0)                  
#>  data.table    1.11.2     2018-05-08 [1] CRAN (R 3.5.0)                  
#>  desc          1.2.0      2018-05-01 [1] CRAN (R 3.5.0)                  
#>  devtools      2.1.0      2019-07-06 [1] CRAN (R 3.6.1)                  
#>  digest        0.6.20     2019-07-04 [1] CRAN (R 3.6.1)                  
#>  dplyr       * 0.8.0.1    2019-02-15 [1] CRAN (R 3.5.2)                  
#>  evaluate      0.14       2019-05-28 [1] CRAN (R 3.6.1)                  
#>  forcats     * 0.3.0      2018-02-19 [1] CRAN (R 3.5.0)                  
#>  foreign       0.8-70     2018-04-23 [1] CRAN (R 3.5.0)                  
#>  fs            1.3.1      2019-05-06 [1] CRAN (R 3.6.1)                  
#>  ggplot2     * 3.2.0      2019-06-16 [1] CRAN (R 3.6.1)                  
#>  glue          1.3.1      2019-03-12 [1] CRAN (R 3.6.1)                  
#>  gtable        0.2.0      2016-02-26 [1] CRAN (R 3.5.0)                  
#>  haven         1.1.1      2018-01-18 [1] CRAN (R 3.5.0)                  
#>  hms           0.4.2      2018-03-10 [1] CRAN (R 3.5.0)                  
#>  htmltools     0.3.6      2017-04-28 [1] CRAN (R 3.5.0)                  
#>  httr          1.3.1      2017-08-20 [1] CRAN (R 3.5.0)                  
#>  jsonlite      1.6        2018-12-07 [1] CRAN (R 3.6.1)                  
#>  knitr         1.23       2019-05-18 [1] CRAN (R 3.6.1)                  
#>  lattice       0.20-38    2018-11-04 [4] CRAN (R 3.5.1)                  
#>  lazyeval      0.2.1      2017-10-29 [1] CRAN (R 3.5.0)                  
#>  lubridate     1.7.4      2018-04-11 [1] CRAN (R 3.5.0)                  
#>  magrittr    * 1.5        2014-11-22 [1] CRAN (R 3.5.0)                  
#>  Matrix        1.2-17     2019-03-22 [4] CRAN (R 3.5.3)                  
#>  memoise       1.1.0      2017-04-21 [1] CRAN (R 3.5.0)                  
#>  mgcv          1.8-24     2018-06-18 [1] CRAN (R 3.5.1)                  
#>  mnormt        1.5-5      2016-10-15 [1] CRAN (R 3.5.0)                  
#>  modelr        0.1.2      2018-05-11 [1] CRAN (R 3.5.0)                  
#>  munsell       0.4.3      2016-02-13 [1] CRAN (R 3.5.0)                  
#>  nlme          3.1-140    2019-05-12 [4] CRAN (R 3.6.0)                  
#>  pillar        1.3.1      2018-12-15 [1] CRAN (R 3.5.2)                  
#>  pkgbuild      1.0.3      2019-03-20 [1] CRAN (R 3.6.1)                  
#>  pkgconfig     2.0.2      2018-08-16 [1] CRAN (R 3.5.2)                  
#>  pkgload       1.0.2      2018-10-29 [1] CRAN (R 3.6.1)                  
#>  plyr          1.8.4      2016-06-08 [1] CRAN (R 3.5.0)                  
#>  prettyunits   1.0.2      2015-07-13 [1] CRAN (R 3.5.2)                  
#>  processx      3.4.0      2019-07-03 [1] CRAN (R 3.6.1)                  
#>  ps            1.3.0      2018-12-21 [1] CRAN (R 3.6.1)                  
#>  psych         1.8.4      2018-05-06 [1] CRAN (R 3.5.0)                  
#>  purrr       * 0.2.4      2017-10-18 [1] CRAN (R 3.5.0)                  
#>  R6            2.2.2      2017-06-17 [1] CRAN (R 3.5.0)                  
#>  Rcpp          1.0.1      2019-03-17 [1] CRAN (R 3.6.1)                  
#>  readr       * 1.1.1      2017-05-16 [1] CRAN (R 3.5.0)                  
#>  readxl        1.1.0      2018-04-20 [1] CRAN (R 3.5.0)                  
#>  remotes       2.1.0      2019-06-24 [1] CRAN (R 3.6.1)                  
#>  reshape2      1.4.3      2017-12-11 [1] CRAN (R 3.5.0)                  
#>  rlang         0.4.0      2019-06-25 [1] CRAN (R 3.6.1)                  
#>  rmarkdown     1.14       2019-07-12 [1] CRAN (R 3.6.1)                  
#>  rprojroot     1.3-2      2018-01-03 [1] CRAN (R 3.5.0)                  
#>  rstudioapi    0.7        2017-09-07 [1] CRAN (R 3.5.0)                  
#>  rticles       0.9.1      2019-07-22 [1] Github (rstudio/rticles@8d56fc6)
#>  rvest         0.3.2      2016-06-17 [1] CRAN (R 3.5.0)                  
#>  scales        0.5.0      2017-08-24 [1] CRAN (R 3.5.0)                  
#>  sessioninfo   1.1.1      2018-11-05 [1] CRAN (R 3.6.1)                  
#>  stringi       1.4.3      2019-03-12 [1] CRAN (R 3.6.1)                  
#>  stringr     * 1.4.0      2019-02-10 [1] CRAN (R 3.6.1)                  
#>  survival    * 2.43-3     2018-11-26 [4] CRAN (R 3.5.1)                  
#>  testthat      2.1.1      2019-04-23 [1] CRAN (R 3.6.1)                  
#>  tibble      * 2.0.1      2019-01-12 [1] CRAN (R 3.5.2)                  
#>  tidyr       * 0.8.1      2018-05-18 [1] CRAN (R 3.5.0)                  
#>  tidyselect    0.2.5      2018-10-11 [1] CRAN (R 3.5.2)                  
#>  tidyverse   * 1.2.1      2017-11-14 [1] CRAN (R 3.5.0)                  
#>  usethis       1.5.1      2019-07-04 [1] CRAN (R 3.6.1)                  
#>  VGAM          1.1-1      2019-02-18 [1] CRAN (R 3.6.1)                  
#>  withr         2.1.2      2018-03-15 [1] CRAN (R 3.5.0)                  
#>  xfun          0.8        2019-06-25 [1] CRAN (R 3.6.1)                  
#>  xml2          1.2.0      2018-01-24 [1] CRAN (R 3.5.0)                  
#>  yaml          2.2.0      2018-07-25 [1] CRAN (R 3.6.1)                  

@@

#> [1] /home/mturgeon/Rlibs
#> [2] /usr/local/lib/R/site-library
#> [3] /usr/lib/R/site-library
#> [4] /usr/lib/R/library

@@

\begin{CodeOutput}
#> Local:    review-max /home/mturgeon/Documents/git_repositories/cbpaper
#> Head:     [c8ac771] 2019-07-22: Merge pull request #5 from sahirbhatnagar/litreview
\end{CodeOutput}
\end{CodeChunk}
